Data Pre-Processing

### 2021-06-18 AST-Framing-Ontario/Data Pre-Processesing.rmd
June 18, 2021
- Initial Sentiment

Load the following packages:
```{r}
library(dplyr)
library(ggraph)
library(ggplot2)
library(igraph)
library(pdftools)
library(readr)
library(reshape2)
library(stringr)
library(text2vec)
library(textdata)
library(tidyr)
library(tidytext)
library(tm) 
library(tools)
library(topicmodels)
library(word2vec)
library(wordcloud)
```

@@

```{r}
# location of manually cleaned .txt documents
cleantxtLocation <- "Cleaned .txt/Academic Papers"

@@

@@

bigram_graph <- bigram_counts %>%
  filter(n > 100) %>%
  graph_from_data_frame()

ggraph(bigram_graph, layout = "fr") +
  geom_edge_link() +
  geom_node_point(color = "lightgreen", size = 4) +
  geom_node_text(aes(label = name), repel = TRUE) + 
  theme_void()

@@

```{r}
v <- sort(rowSums(matrix1), decreasing= TRUE)
d <- data.frame(word = names(v), freq=v)
set.seed(4321)
wordcloud(d$word, d$freq, min.freq = 10, max.words = 50, random.order = FALSE, rot.per = 0.5, random.color = TRUE)
```

@@

>>>>

Load the following packages:
```{r}
library(dplyr)
library(ggraph)
library(ggplot2)
library(igraph)
library(pdftools)
library(readr)
library(reshape2)
library(stringr)
library(text2vec)
library(textdata)
library(tidyr)
library(tidytext)
library(tm) 
library(tools)
library(topicmodels)
library(widyr)
library(word2vec)
library(wordcloud)
```

@@

```{r}
# location of manually cleaned .txt documents
cleantxtLocation <- "Cleaned .txt/Policy"

@@

bigram_graph <- bigram_counts %>%
  filter(n > 10) %>%
  graph_from_data_frame()

@@

ggraph(bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightgreen", size = 4) +
  geom_node_text(aes(label = name), repel = TRUE) + 
  theme_void()

@@

```{r}
v <- sort(rowSums(matrix1), decreasing= TRUE)
d <- data.frame(word = names(v), freq=v)
set.seed(4321)
wordcloud(d$word, d$freq, min.freq = 25, max.words = 50, random.order = FALSE, rot.per = 0.5, random.color = TRUE)
```

@@

```{r}
library(widyr)

words <- td_corpus %>%
  unnest_tokens(word, text, token = "ngrams", n = 1)

# word_count <- words %>%
#   count(word, sort = TRUE)

word_pairs <- words %>%
  pairwise_count(word, id, sort = TRUE)

word_pairs %>%
  filter(item1 == "traffic")

```
```{r}
word_pairs %>%
  filter(item1 %in% c("traffic", "safety", "urban", "street")) %>%
  group_by(item1) %>%
  slice_max(n, n = 10) %>%
  ungroup() %>%
  mutate(item2 = reorder(item2, n)) %>%
  ggplot(aes(item2, n)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ item1, scales = "free") +
  coord_flip()
```

```{r}
word_cors <- words %>% 
  group_by(word) %>% 
  filter(n() >= 10) %>%
  pairwise_cor(word, id, sort = TRUE)

word_cors %>%
  filter(item1 == "traffic")

word_cors %>%
  filter(item1 == "safety")

word_cors %>%
  filter(item1 == "urban")

word_cors %>%
  filter(item1 == "car")

word_cors %>%
  filter(item1 == "transit")

word_cors %>%
  filter(item1 == "independent")

word_cors %>%
  filter(item1 == "transit")

word_cors %>%
  filter(item1 == "street")

word_cors %>%
  filter(item1 == "age")

word_cors %>%
  filter(item1 == "parental")

```
```{r}
word_cors %>%
  filter(item1 %in% c("traffic", "independent", "safety", "urban", "density", "street")) %>%
  group_by(item1) %>%
  slice_max(correlation, n = 7) %>%
  ungroup() %>%
  mutate(item2 = reorder(item2, correlation)) %>%
  ggplot(aes(item2, correlation)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ item1, scales = "free") +
  coord_flip()
```
